Heuristics and A* implementations

### 2020-05-19 paper/paper.tex
Test whether goals are a subset of the state when planning
Explain Dijkstra and A* on paper

\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{listings}
\usepackage{xcolor}

@@

\subsection{Blocksworld}
\subsection{Dinner}
\subsection{Dompteur}
\subsection{DWR}
\subsection{Logistics}
\subsection{TSP}

@@

The first step to get the next reachable state is to filter only the actions applicable to the current state and obtain the effects of those actions (line~\ref{line:new_reachable:h_add_python}). After that, the cost of each effect is calculated and added to the variable \textit{cost} (line~\ref{line:add_effect_cost:h_add_python}).

@@

>>>>

\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{forest}

@@

\subsection{Blocksworld}
\subsection{Dinner}
\subsection{Dompteur}
\subsection{DWR - Dock Worker Robots}
\subsection{Logistics}
\subsection{TSP - Travel Sales Person}

@@

The first step to get the next reachable state is to filter only the actions applicable to the current state and obtain the effects of those actions (line~\ref{line:new_reachable:h_add_python}). After that, the cost of each effect is calculated and added to the variable \textit{costs} (line~\ref{line:add_effect_cost:h_add_python}). The cost of the effect will be the sum of the costs of the preconditions plus 1, because it is the next step in the search tree.

@@

\section{Solver using A* and $h_{max}$}

A solver is responsible for finding the best path to achieve the goal. In STRIPS planning, the best path is the path that performs the least actions to achieve all goals. In this section, I will show how the A* differs from the Dijkstra algorithm and also an algorithm to search for the shortest path using A* search, guided by the $h_{max}$ heuristic.

\subsection{Dijkstra and A*}

A* is based on the Dijkstra algorithm. In a nutshell, Dijkstra's algorithm searches for the node in the tree that has the lowest cost. The Figure~\ref{fig:dijkstra-tree} helps to understand the Dijkstra's algorithm. Our goal is to be in city E, starting from city A.

\begin{figure}
  \centering
  \begin{forest}
    [A (0)
      [B (40)
          [E (20)]
        ]
        [C (30)
          [D (10)
              [E (15)]
            ]
        ]
    ]
  \end{forest}
  \caption{Dijkstra search tree}\label{fig:dijkstra-tree}
\end{figure}

The distance between cities A and B is 40 kilometers. Therefore, Dijkstra's algorithm will choose the path from city A to C, since the distance is shorter. In the next step, the algorithm have two possible nodes to expand: B and D. As the distance from city C to D is less than city A to B, the algorithm will choose the path from city C to D. Following the same logic, in the end, the algorithm will choose the path from city D to E, reaching the goal.

From the Dijkstra's algorithm, the A* algorithm adds a heuristic value to the cost of moving from a city to another, for example. In Figure~\ref{fig:a-star-tree}, I show an example of heuristic: the straight line distance between two cities. The straight line between cities C and E, for example, I considered $\inf$, because I cannot travel between these two cities without going through city D.

Now, the distance between cities A and B is 50 kilometers and between cities A and C is 55 kilometers. Therefore, the A* algorithm will choose the path between cities A and B. In the next step, the algorithm chooses the path between B and E, because the distance, considering the heuristic, is shortest. A bad heuristic will guide the A* algorithm to the wrong direction. However, with good heuristics, A* algorithm needs to expand fewer nodes to reach the goal.

\begin{figure}
  \centering
  \begin{forest}
    [A (0)
      [B (40-10)
          [E (20-15)]
        ]
        [C (30-25)
          [D (10-7)
              [E (15-11)]
            ]
        ]
    ]
  \end{forest}
  \caption{A* search tree}\label{fig:a-star-tree}
\end{figure}

\subsection{Solver Explanation}

The solver uses the A* algorithm, guided by the $h_{max}$ heuristic. To implement the search, I used the \textit{heapq} and the \textit{pddl} packages. The first was used for the priority queue and the second for parsing the PDDL domain file and problem file.

explain priority queue

get some lines of the implentation and explain
